Measuring Subgroup Preferences in Conjoint Experiments

### 2019-05-24 manuscript.tex
final PA submission

\usepackage{alltt}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mathpazo}
%\usepackage{times}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage[normalem]{ulem}
\usepackage{sectsty}
\subsectionfont{\normalfont\large\underline}
\usepackage{floatrow}
\floatsetup[figure]{capposition=top}
\floatsetup[table]{capposition=top}

\title{Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}}
\author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/tkr_replication-1} \caption[Replication of Results for `Candidate Sex' Feature from Teele et al]{Replication of Results for `Candidate Sex' Feature from Teele et al. (2018) Candidate Experiment using Full Sample and Subgroup AMCEs and MMs}\label{fig:tkr_replication}
\end{figure}

@@

% latex table generated in R 3.5.3 by xtable 1.8-3 package
% Tue Apr 16 22:40:04 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Military Service & Did Not Serve & 0.00 &  &  \\ 
  Military Service & Served & 0.09 & 0.02 & 4.95 \\ 
  Religion & None & 0.00 &  &  \\ 
  Religion & Jewish & -0.04 & 0.03 & -1.42 \\ 
  Religion & Catholic & -0.02 & 0.03 & -0.56 \\ 
  Religion & Mainline protestant & -0.01 & 0.03 & -0.48 \\ 
  Religion & Evangelical protestant & -0.12 & 0.03 & -3.78 \\ 
  Religion & Mormon & -0.14 & 0.03 & -4.46 \\ 
  College & No BA & 0.00 &  &  \\ 
  College & Baptist college & 0.14 & 0.03 & 4.82 \\ 
  College & Community college & 0.15 & 0.03 & 5.17 \\ 
  College & State university & 0.19 & 0.03 & 6.77 \\ 
  College & Small college & 0.18 & 0.03 & 6.50 \\ 
  College & Ivy League university & 0.27 & 0.03 & 9.26 \\ 
  Profession & Business owner & 0.00 &  &  \\ 
  Profession & Lawyer & -0.02 & 0.03 & -0.71 \\ 
  Profession & Doctor & -0.02 & 0.03 & -0.53 \\ 
  Profession & High school teacher & -0.04 & 0.03 & -1.42 \\ 
  Profession & Farmer & -0.09 & 0.03 & -2.94 \\ 
  Profession & Car dealer & -0.23 & 0.03 & -7.24 \\ 
  Income & 32K & 0.00 &  &  \\ 
  Income & 54K & 0.02 & 0.03 & 0.82 \\ 
  Income & 65K & 0.06 & 0.03 & 2.26 \\ 
  Income & 92K & 0.03 & 0.03 & 1.12 \\ 
  Income & 210K & 0.07 & 0.03 & 2.41 \\ 
  Income & 5.1M & 0.01 & 0.03 & 0.25 \\ 
  Race/Ethnicity & White & 0.00 &  &  \\ 
  Race/Ethnicity & Native American & 0.02 & 0.03 & 0.85 \\ 
  Race/Ethnicity & Black & 0.03 & 0.03 & 1.22 \\ 
  Race/Ethnicity & Hispanic & -0.02 & 0.03 & -0.84 \\ 
  Race/Ethnicity & Caucasian & 0.00 & 0.03 & 0.18 \\ 
  Race/Ethnicity & Asian American & 0.04 & 0.03 & 1.51 \\ 
  Age & 36 & 0.00 &  &  \\ 
  Age & 45 & 0.03 & 0.03 & 0.88 \\ 
  Age & 52 & 0.02 & 0.03 & 0.78 \\ 
  Age & 60 & 0.00 & 0.03 & 0.14 \\ 
  Age & 68 & -0.06 & 0.03 & -2.17 \\ 
  Age & 75 & -0.15 & 0.03 & -5.06 \\ 
  Gender & Male & 0.00 &  &  \\ 
  Gender & Female & 0.00 & 0.02 & 0.09 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

@@

% latex table generated in R 3.5.3 by xtable 1.8-3 package
% Tue Apr 16 22:40:05 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Military Service & Did Not Serve & 0.46 & 0.01 & -3.54 \\ 
  Military Service & Served & 0.54 & 0.01 & 3.55 \\ 
  Religion & None & 0.56 & 0.02 & 2.73 \\ 
  Religion & Jewish & 0.52 & 0.02 & 0.96 \\ 
  Religion & Catholic & 0.53 & 0.02 & 1.24 \\ 
  Religion & Mainline protestant & 0.54 & 0.02 & 2.06 \\ 
  Religion & Evangelical protestant & 0.44 & 0.02 & -3.05 \\ 
  Religion & Mormon & 0.42 & 0.02 & -4.04 \\ 
  College & No BA & 0.34 & 0.02 & -8.11 \\ 
  College & Baptist college & 0.48 & 0.02 & -0.83 \\ 
  College & Community college & 0.49 & 0.02 & -0.39 \\ 
  College & State university & 0.53 & 0.02 & 1.39 \\ 
  College & Small college & 0.52 & 0.02 & 0.99 \\ 
  College & Ivy League university & 0.62 & 0.02 & 6.27 \\ 
  Profession & Business owner & 0.57 & 0.02 & 3.35 \\ 
  Profession & Lawyer & 0.55 & 0.02 & 2.20 \\ 
  Profession & Doctor & 0.54 & 0.02 & 2.08 \\ 
  Profession & High school teacher & 0.53 & 0.02 & 1.44 \\ 
  Profession & Farmer & 0.48 & 0.02 & -0.98 \\ 
  Profession & Car dealer & 0.33 & 0.02 & -8.64 \\ 
  Income & 32K & 0.46 & 0.02 & -1.89 \\ 
  Income & 54K & 0.49 & 0.02 & -0.65 \\ 
  Income & 65K & 0.53 & 0.02 & 1.33 \\ 
  Income & 92K & 0.51 & 0.02 & 0.46 \\ 
  Income & 210K & 0.54 & 0.02 & 1.94 \\ 
  Income & 5.1M & 0.47 & 0.02 & -1.26 \\ 
  Race/Ethnicity & White & 0.48 & 0.02 & -0.88 \\ 
  Race/Ethnicity & Native American & 0.52 & 0.02 & 0.96 \\ 
  Race/Ethnicity & Black & 0.52 & 0.02 & 0.85 \\ 
  Race/Ethnicity & Hispanic & 0.47 & 0.02 & -1.59 \\ 
  Race/Ethnicity & Caucasian & 0.49 & 0.02 & -0.53 \\ 
  Race/Ethnicity & Asian American & 0.52 & 0.02 & 1.14 \\ 
  Age & 36 & 0.53 & 0.02 & 1.43 \\ 
  Age & 45 & 0.55 & 0.02 & 2.21 \\ 
  Age & 52 & 0.56 & 0.02 & 3.18 \\ 
  Age & 60 & 0.53 & 0.02 & 1.40 \\ 
  Age & 68 & 0.45 & 0.02 & -2.31 \\ 
  Age & 75 & 0.38 & 0.02 & -5.99 \\ 
  Gender & Male & 0.50 & 0.01 & -0.07 \\ 
  Gender & Female & 0.50 & 0.01 & 0.07 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

@@

% latex table generated in R 3.5.3 by xtable 1.8-3 package
% Tue Apr 16 22:40:09 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Gender & female & 0.00 &  &  \\ 
  Gender & male & -0.03 & 0.01 & -3.25 \\ 
  Education & No formal education & 0.00 &  &  \\ 
  Education & Equivalent to completing fourth grade & 0.03 & 0.01 & 2.22 \\ 
  Education & Equivalent to completing eighth grade & 0.06 & 0.01 & 3.86 \\ 
  Education & Equivalent to completing high school & 0.12 & 0.01 & 7.98 \\ 
  Education & Equivalent to completing two years of college & 0.16 & 0.02 & 7.12 \\ 
  Education & Equivalent to completing a college degree & 0.19 & 0.02 & 8.26 \\ 
  Education & Equivalent to completing a graduate degree & 0.18 & 0.02 & 10.41 \\ 
  Language Skills & spoke fluent English & 0.00 &  &  \\ 
  Language Skills & spoke broken English & -0.06 & 0.01 & -4.98 \\ 
  Language Skills & tried to speak English but was unable & -0.13 & 0.01 & -11.11 \\ 
  Language Skills & spoke [language] and used an interpreter & -0.16 & 0.01 & -13.78 \\ 
  Country of Origin & India & 0.00 &  &  \\ 
  Country of Origin & Germany & 0.05 & 0.02 & 2.66 \\ 
  Country of Origin & France & 0.03 & 0.02 & 1.53 \\ 
  Country of Origin & Mexico & 0.01 & 0.02 & 0.59 \\ 
  Country of Origin & Philippines & 0.03 & 0.02 & 1.91 \\ 
  Country of Origin & Poland & 0.03 & 0.02 & 1.83 \\ 
  Country of Origin & China & -0.02 & 0.02 & -0.81 \\ 
  Country of Origin & Sudan & -0.04 & 0.02 & -2.01 \\ 
  Country of Origin & Somalia & -0.05 & 0.02 & -2.29 \\ 
  Country of Origin & Iraq & -0.11 & 0.02 & -5.56 \\ 
  Job & Janitor & 0.00 &  &  \\ 
  Job & Waiter & -0.01 & 0.02 & -0.41 \\ 
  Job & Child care provider & 0.01 & 0.02 & 0.89 \\ 
  Job & Gardener & 0.01 & 0.02 & 0.78 \\ 
  Job & Financial analyst & 0.06 & 0.03 & 2.17 \\ 
  Job & Construction worker & 0.04 & 0.02 & 2.26 \\ 
  Job & Teacher & 0.07 & 0.02 & 4.39 \\ 
  Job & Computer programmer & 0.08 & 0.03 & 2.76 \\ 
  Job & Nurse & 0.08 & 0.02 & 5.08 \\ 
  Job & Research scientist & 0.13 & 0.03 & 4.44 \\ 
  Job & Doctor & 0.16 & 0.03 & 5.49 \\ 
  Job Experience & No job training or prior experience & 0.00 &  &  \\ 
  Job Experience & One or two years of job training and experience & 0.07 & 0.01 & 5.92 \\ 
  Job Experience & Three to five years of job training and experience & 0.11 & 0.01 & 9.32 \\ 
  Job Experience & More than five years of job training and experience & 0.11 & 0.01 & 9.96 \\ 
  Job Plans & Has a contract with a U.S. employer & 0.00 &  &  \\ 
  Job Plans & Does not have a contract with a U.S. employer & -0.10 & 0.01 & -8.50 \\ 
  Job Plans & Will look for work after arriving in the U.S. & -0.12 & 0.01 & -10.69 \\ 
  Job Plans & Has no plans to look for work at this time & -0.28 & 0.01 & -23.91 \\ 
  Reason for Application & Reunite with family members already in the U.S. & 0.00 &  &  \\ 
  Reason for Application & Seek better job in U.S. & -0.04 & 0.01 & -4.37 \\ 
  Reason for Application & Escape political/religious persecution & 0.06 & 0.02 & 3.58 \\ 
  Prior Entry & Never been to the U.S. & 0.00 &  &  \\ 
  Prior Entry & Entered U.S. once before on a tourist visa & 0.06 & 0.01 & 4.49 \\ 
  Prior Entry & Has visited the U.S. many times before on tourist visas & 0.05 & 0.01 & 4.24 \\ 
  Prior Entry & Spent six months with family members in the U.S & 0.08 & 0.01 & 5.98 \\ 
  Prior Entry & Entered the U.S. once before without legal authorization & -0.11 & 0.01 & -8.45 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

@@

% latex table generated in R 3.5.3 by xtable 1.8-3 package
% Tue Apr 16 22:40:15 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Gender & female & 0.51 & 0.01 & 1.99 \\ 
  Gender & male & 0.49 & 0.01 & -2.03 \\ 
  Education & No formal education & 0.39 & 0.01 & -10.04 \\ 
  Education & Equivalent to completing fourth grade & 0.42 & 0.01 & -7.08 \\ 
  Education & Equivalent to completing eighth grade & 0.44 & 0.01 & -5.00 \\ 
  Education & Equivalent to completing high school & 0.51 & 0.01 & 0.67 \\ 
  Education & Equivalent to completing two years of college & 0.57 & 0.01 & 5.92 \\ 
  Education & Equivalent to completing a college degree & 0.59 & 0.01 & 8.00 \\ 
  Education & Equivalent to completing a graduate degree & 0.58 & 0.01 & 7.40 \\ 
  Language Skills & spoke fluent English & 0.59 & 0.01 & 10.63 \\ 
  Language Skills & spoke broken English & 0.53 & 0.01 & 3.07 \\ 
  Language Skills & tried to speak English but was unable & 0.46 & 0.01 & -4.83 \\ 
  Language Skills & spoke [language] and used an interpreter & 0.42 & 0.01 & -8.98 \\ 
  Country of Origin & India & 0.50 & 0.01 & 0.13 \\ 
  Country of Origin & Germany & 0.54 & 0.01 & 3.22 \\ 
  Country of Origin & France & 0.52 & 0.01 & 1.26 \\ 
  Country of Origin & Mexico & 0.51 & 0.01 & 0.92 \\ 
  Country of Origin & Philippines & 0.53 & 0.01 & 2.36 \\ 
  Country of Origin & Poland & 0.53 & 0.01 & 2.01 \\ 
  Country of Origin & China & 0.50 & 0.01 & -0.03 \\ 
  Country of Origin & Sudan & 0.48 & 0.01 & -1.42 \\ 
  Country of Origin & Somalia & 0.47 & 0.01 & -2.01 \\ 
  Country of Origin & Iraq & 0.41 & 0.01 & -6.76 \\ 
  Job & Janitor & 0.45 & 0.01 & -4.20 \\ 
  Job & Waiter & 0.45 & 0.01 & -4.56 \\ 
  Job & Child care provider & 0.46 & 0.01 & -3.50 \\ 
  Job & Gardener & 0.46 & 0.01 & -3.11 \\ 
  Job & Financial analyst & 0.57 & 0.02 & 3.16 \\ 
  Job & Construction worker & 0.48 & 0.01 & -1.23 \\ 
  Job & Teacher & 0.52 & 0.01 & 1.49 \\ 
  Job & Computer programmer & 0.58 & 0.02 & 4.01 \\ 
  Job & Nurse & 0.53 & 0.01 & 2.82 \\ 
  Job & Research scientist & 0.64 & 0.02 & 6.82 \\ 
  Job & Doctor & 0.67 & 0.02 & 8.53 \\ 
  Job Experience & No job training or prior experience & 0.43 & 0.01 & -8.27 \\ 
  Job Experience & One or two years of job training and experience & 0.49 & 0.01 & -1.05 \\ 
  Job Experience & Three to five years of job training and experience & 0.54 & 0.01 & 4.33 \\ 
  Job Experience & More than five years of job training and experience & 0.54 & 0.01 & 4.92 \\ 
  Job Plans & Has a contract with a U.S. employer & 0.63 & 0.01 & 15.40 \\ 
  Job Plans & Does not have a contract with a U.S. employer & 0.53 & 0.01 & 3.47 \\ 
  Job Plans & Will look for work after arriving in the U.S. & 0.51 & 0.01 & 0.78 \\ 
  Job Plans & Has no plans to look for work at this time & 0.34 & 0.01 & -19.86 \\ 
  Reason for Application & Reunite with family members already in the U.S. & 0.52 & 0.01 & 3.00 \\ 
  Reason for Application & Seek better job in U.S. & 0.48 & 0.01 & -3.76 \\ 
  Reason for Application & Escape political/religious persecution & 0.52 & 0.01 & 1.40 \\ 
  Prior Entry & Never been to the U.S. & 0.49 & 0.01 & -1.47 \\ 
  Prior Entry & Entered U.S. once before on a tourist visa & 0.54 & 0.01 & 4.37 \\ 
  Prior Entry & Has visited the U.S. many times before on tourist visas & 0.54 & 0.01 & 4.50 \\ 
  Prior Entry & Spent six months with family members in the U.S & 0.56 & 0.01 & 6.24 \\ 
  Prior Entry & Entered the U.S. once before without legal authorization & 0.37 & 0.01 & -13.96 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

>>>>

\usepackage{alltt}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mathpazo}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage[normalem]{ulem}
\usepackage{sectsty}
\subsectionfont{\normalfont\large\underline}
\usepackage{floatrow}
\usepackage[hidelinks]{hyperref}
\floatsetup[figure]{capposition=top}
\floatsetup[table]{capposition=top}

\title{Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript. Replication data and code for this article are available from the \textit{Political Analysis} Dataverse: \url{https://doi.org/10.7910/DVN/ARHZU4}. This work was funded, in part, by the United Kingdom Economic and Social Research Council (Grant ES/R000573/1).}
}
\author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/tkr_replication-1} \caption[Replication of Results for `Candidate Sex' Feature from Teele et al]{Replication of Results for `Candidate Sex' Feature from Teele et al. (2018) Candidate Experiment using Full Sample AMCEs and MMs and Subgroup AMCEs and MMs for Democrats and Republicans}\label{fig:tkr_replication}
\end{figure}

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Fri May 24 16:19:30 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Military Service & Did Not Serve & 0.00 &  &  \\ 
  Military Service & Served & 0.09 & 0.02 & 4.95 \\ 
  Religion & None & 0.00 &  &  \\ 
  Religion & Jewish & -0.04 & 0.03 & -1.42 \\ 
  Religion & Catholic & -0.02 & 0.03 & -0.56 \\ 
  Religion & Mainline protestant & -0.01 & 0.03 & -0.48 \\ 
  Religion & Evangelical protestant & -0.12 & 0.03 & -3.78 \\ 
  Religion & Mormon & -0.14 & 0.03 & -4.46 \\ 
  College & No BA & 0.00 &  &  \\ 
  College & Baptist college & 0.14 & 0.03 & 4.82 \\ 
  College & Community college & 0.15 & 0.03 & 5.17 \\ 
  College & State university & 0.19 & 0.03 & 6.77 \\ 
  College & Small college & 0.18 & 0.03 & 6.50 \\ 
  College & Ivy League university & 0.27 & 0.03 & 9.26 \\ 
  Profession & Business owner & 0.00 &  &  \\ 
  Profession & Lawyer & -0.02 & 0.03 & -0.71 \\ 
  Profession & Doctor & -0.02 & 0.03 & -0.53 \\ 
  Profession & High school teacher & -0.04 & 0.03 & -1.42 \\ 
  Profession & Farmer & -0.09 & 0.03 & -2.94 \\ 
  Profession & Car dealer & -0.23 & 0.03 & -7.24 \\ 
  Income & 32K & 0.00 &  &  \\ 
  Income & 54K & 0.02 & 0.03 & 0.82 \\ 
  Income & 65K & 0.06 & 0.03 & 2.26 \\ 
  Income & 92K & 0.03 & 0.03 & 1.12 \\ 
  Income & 210K & 0.07 & 0.03 & 2.41 \\ 
  Income & 5.1M & 0.01 & 0.03 & 0.25 \\ 
  Race/Ethnicity & White & 0.00 &  &  \\ 
  Race/Ethnicity & Native American & 0.02 & 0.03 & 0.85 \\ 
  Race/Ethnicity & Black & 0.03 & 0.03 & 1.22 \\ 
  Race/Ethnicity & Hispanic & -0.02 & 0.03 & -0.84 \\ 
  Race/Ethnicity & Caucasian & 0.00 & 0.03 & 0.18 \\ 
  Race/Ethnicity & Asian American & 0.04 & 0.03 & 1.51 \\ 
  Age & 36 & 0.00 &  &  \\ 
  Age & 45 & 0.03 & 0.03 & 0.88 \\ 
  Age & 52 & 0.02 & 0.03 & 0.78 \\ 
  Age & 60 & 0.00 & 0.03 & 0.14 \\ 
  Age & 68 & -0.06 & 0.03 & -2.17 \\ 
  Age & 75 & -0.15 & 0.03 & -5.06 \\ 
  Gender & Male & 0.00 &  &  \\ 
  Gender & Female & 0.00 & 0.02 & 0.09 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Fri May 24 16:19:31 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Military Service & Did Not Serve & 0.46 & 0.01 & -3.54 \\ 
  Military Service & Served & 0.54 & 0.01 & 3.55 \\ 
  Religion & None & 0.56 & 0.02 & 2.73 \\ 
  Religion & Jewish & 0.52 & 0.02 & 0.96 \\ 
  Religion & Catholic & 0.53 & 0.02 & 1.24 \\ 
  Religion & Mainline protestant & 0.54 & 0.02 & 2.06 \\ 
  Religion & Evangelical protestant & 0.44 & 0.02 & -3.05 \\ 
  Religion & Mormon & 0.42 & 0.02 & -4.04 \\ 
  College & No BA & 0.34 & 0.02 & -8.11 \\ 
  College & Baptist college & 0.48 & 0.02 & -0.83 \\ 
  College & Community college & 0.49 & 0.02 & -0.39 \\ 
  College & State university & 0.53 & 0.02 & 1.39 \\ 
  College & Small college & 0.52 & 0.02 & 0.99 \\ 
  College & Ivy League university & 0.62 & 0.02 & 6.27 \\ 
  Profession & Business owner & 0.57 & 0.02 & 3.35 \\ 
  Profession & Lawyer & 0.55 & 0.02 & 2.20 \\ 
  Profession & Doctor & 0.54 & 0.02 & 2.08 \\ 
  Profession & High school teacher & 0.53 & 0.02 & 1.44 \\ 
  Profession & Farmer & 0.48 & 0.02 & -0.98 \\ 
  Profession & Car dealer & 0.33 & 0.02 & -8.64 \\ 
  Income & 32K & 0.46 & 0.02 & -1.89 \\ 
  Income & 54K & 0.49 & 0.02 & -0.65 \\ 
  Income & 65K & 0.53 & 0.02 & 1.33 \\ 
  Income & 92K & 0.51 & 0.02 & 0.46 \\ 
  Income & 210K & 0.54 & 0.02 & 1.94 \\ 
  Income & 5.1M & 0.47 & 0.02 & -1.26 \\ 
  Race/Ethnicity & White & 0.48 & 0.02 & -0.88 \\ 
  Race/Ethnicity & Native American & 0.52 & 0.02 & 0.96 \\ 
  Race/Ethnicity & Black & 0.52 & 0.02 & 0.85 \\ 
  Race/Ethnicity & Hispanic & 0.47 & 0.02 & -1.59 \\ 
  Race/Ethnicity & Caucasian & 0.49 & 0.02 & -0.53 \\ 
  Race/Ethnicity & Asian American & 0.52 & 0.02 & 1.14 \\ 
  Age & 36 & 0.53 & 0.02 & 1.43 \\ 
  Age & 45 & 0.55 & 0.02 & 2.21 \\ 
  Age & 52 & 0.56 & 0.02 & 3.18 \\ 
  Age & 60 & 0.53 & 0.02 & 1.40 \\ 
  Age & 68 & 0.45 & 0.02 & -2.31 \\ 
  Age & 75 & 0.38 & 0.02 & -5.99 \\ 
  Gender & Male & 0.50 & 0.01 & -0.07 \\ 
  Gender & Female & 0.50 & 0.01 & 0.07 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Fri May 24 16:19:34 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Gender & female & 0.00 &  &  \\ 
  Gender & male & -0.03 & 0.01 & -3.25 \\ 
  Education & No formal education & 0.00 &  &  \\ 
  Education & Equivalent to completing fourth grade & 0.03 & 0.01 & 2.22 \\ 
  Education & Equivalent to completing eighth grade & 0.06 & 0.01 & 3.86 \\ 
  Education & Equivalent to completing high school & 0.12 & 0.01 & 7.98 \\ 
  Education & Equivalent to completing two years of college & 0.16 & 0.02 & 7.12 \\ 
  Education & Equivalent to completing a college degree & 0.19 & 0.02 & 8.26 \\ 
  Education & Equivalent to completing a graduate degree & 0.18 & 0.02 & 10.41 \\ 
  Language Skills & spoke fluent English & 0.00 &  &  \\ 
  Language Skills & spoke broken English & -0.06 & 0.01 & -4.98 \\ 
  Language Skills & tried to speak English but was unable & -0.13 & 0.01 & -11.11 \\ 
  Language Skills & spoke [language] and used an interpreter & -0.16 & 0.01 & -13.78 \\ 
  Country of Origin & India & 0.00 &  &  \\ 
  Country of Origin & Germany & 0.05 & 0.02 & 2.66 \\ 
  Country of Origin & France & 0.03 & 0.02 & 1.53 \\ 
  Country of Origin & Mexico & 0.01 & 0.02 & 0.59 \\ 
  Country of Origin & Philippines & 0.03 & 0.02 & 1.91 \\ 
  Country of Origin & Poland & 0.03 & 0.02 & 1.83 \\ 
  Country of Origin & China & -0.02 & 0.02 & -0.81 \\ 
  Country of Origin & Sudan & -0.04 & 0.02 & -2.01 \\ 
  Country of Origin & Somalia & -0.05 & 0.02 & -2.29 \\ 
  Country of Origin & Iraq & -0.11 & 0.02 & -5.56 \\ 
  Job & Janitor & 0.00 &  &  \\ 
  Job & Waiter & -0.01 & 0.02 & -0.41 \\ 
  Job & Child care provider & 0.01 & 0.02 & 0.89 \\ 
  Job & Gardener & 0.01 & 0.02 & 0.78 \\ 
  Job & Financial analyst & 0.06 & 0.03 & 2.17 \\ 
  Job & Construction worker & 0.04 & 0.02 & 2.26 \\ 
  Job & Teacher & 0.07 & 0.02 & 4.39 \\ 
  Job & Computer programmer & 0.08 & 0.03 & 2.76 \\ 
  Job & Nurse & 0.08 & 0.02 & 5.08 \\ 
  Job & Research scientist & 0.13 & 0.03 & 4.44 \\ 
  Job & Doctor & 0.16 & 0.03 & 5.49 \\ 
  Job Experience & No job training or prior experience & 0.00 &  &  \\ 
  Job Experience & One or two years of job training and experience & 0.07 & 0.01 & 5.92 \\ 
  Job Experience & Three to five years of job training and experience & 0.11 & 0.01 & 9.32 \\ 
  Job Experience & More than five years of job training and experience & 0.11 & 0.01 & 9.96 \\ 
  Job Plans & Has a contract with a U.S. employer & 0.00 &  &  \\ 
  Job Plans & Does not have a contract with a U.S. employer & -0.10 & 0.01 & -8.50 \\ 
  Job Plans & Will look for work after arriving in the U.S. & -0.12 & 0.01 & -10.69 \\ 
  Job Plans & Has no plans to look for work at this time & -0.28 & 0.01 & -23.91 \\ 
  Reason for Application & Reunite with family members already in the U.S. & 0.00 &  &  \\ 
  Reason for Application & Seek better job in U.S. & -0.04 & 0.01 & -4.37 \\ 
  Reason for Application & Escape political/religious persecution & 0.06 & 0.02 & 3.58 \\ 
  Prior Entry & Never been to the U.S. & 0.00 &  &  \\ 
  Prior Entry & Entered U.S. once before on a tourist visa & 0.06 & 0.01 & 4.49 \\ 
  Prior Entry & Has visited the U.S. many times before on tourist visas & 0.05 & 0.01 & 4.24 \\ 
  Prior Entry & Spent six months with family members in the U.S & 0.08 & 0.01 & 5.98 \\ 
  Prior Entry & Entered the U.S. once before without legal authorization & -0.11 & 0.01 & -8.45 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Fri May 24 16:19:41 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Gender & female & 0.51 & 0.01 & 1.99 \\ 
  Gender & male & 0.49 & 0.01 & -2.03 \\ 
  Education & No formal education & 0.39 & 0.01 & -10.04 \\ 
  Education & Equivalent to completing fourth grade & 0.42 & 0.01 & -7.08 \\ 
  Education & Equivalent to completing eighth grade & 0.44 & 0.01 & -5.00 \\ 
  Education & Equivalent to completing high school & 0.51 & 0.01 & 0.67 \\ 
  Education & Equivalent to completing two years of college & 0.57 & 0.01 & 5.92 \\ 
  Education & Equivalent to completing a college degree & 0.59 & 0.01 & 8.00 \\ 
  Education & Equivalent to completing a graduate degree & 0.58 & 0.01 & 7.40 \\ 
  Language Skills & spoke fluent English & 0.59 & 0.01 & 10.63 \\ 
  Language Skills & spoke broken English & 0.53 & 0.01 & 3.07 \\ 
  Language Skills & tried to speak English but was unable & 0.46 & 0.01 & -4.83 \\ 
  Language Skills & spoke [language] and used an interpreter & 0.42 & 0.01 & -8.98 \\ 
  Country of Origin & India & 0.50 & 0.01 & 0.13 \\ 
  Country of Origin & Germany & 0.54 & 0.01 & 3.22 \\ 
  Country of Origin & France & 0.52 & 0.01 & 1.26 \\ 
  Country of Origin & Mexico & 0.51 & 0.01 & 0.92 \\ 
  Country of Origin & Philippines & 0.53 & 0.01 & 2.36 \\ 
  Country of Origin & Poland & 0.53 & 0.01 & 2.01 \\ 
  Country of Origin & China & 0.50 & 0.01 & -0.03 \\ 
  Country of Origin & Sudan & 0.48 & 0.01 & -1.42 \\ 
  Country of Origin & Somalia & 0.47 & 0.01 & -2.01 \\ 
  Country of Origin & Iraq & 0.41 & 0.01 & -6.76 \\ 
  Job & Janitor & 0.45 & 0.01 & -4.20 \\ 
  Job & Waiter & 0.45 & 0.01 & -4.56 \\ 
  Job & Child care provider & 0.46 & 0.01 & -3.50 \\ 
  Job & Gardener & 0.46 & 0.01 & -3.11 \\ 
  Job & Financial analyst & 0.57 & 0.02 & 3.16 \\ 
  Job & Construction worker & 0.48 & 0.01 & -1.23 \\ 
  Job & Teacher & 0.52 & 0.01 & 1.49 \\ 
  Job & Computer programmer & 0.58 & 0.02 & 4.01 \\ 
  Job & Nurse & 0.53 & 0.01 & 2.82 \\ 
  Job & Research scientist & 0.64 & 0.02 & 6.82 \\ 
  Job & Doctor & 0.67 & 0.02 & 8.53 \\ 
  Job Experience & No job training or prior experience & 0.43 & 0.01 & -8.27 \\ 
  Job Experience & One or two years of job training and experience & 0.49 & 0.01 & -1.05 \\ 
  Job Experience & Three to five years of job training and experience & 0.54 & 0.01 & 4.33 \\ 
  Job Experience & More than five years of job training and experience & 0.54 & 0.01 & 4.92 \\ 
  Job Plans & Has a contract with a U.S. employer & 0.63 & 0.01 & 15.40 \\ 
  Job Plans & Does not have a contract with a U.S. employer & 0.53 & 0.01 & 3.47 \\ 
  Job Plans & Will look for work after arriving in the U.S. & 0.51 & 0.01 & 0.78 \\ 
  Job Plans & Has no plans to look for work at this time & 0.34 & 0.01 & -19.86 \\ 
  Reason for Application & Reunite with family members already in the U.S. & 0.52 & 0.01 & 3.00 \\ 
  Reason for Application & Seek better job in U.S. & 0.48 & 0.01 & -3.76 \\ 
  Reason for Application & Escape political/religious persecution & 0.52 & 0.01 & 1.40 \\ 
  Prior Entry & Never been to the U.S. & 0.49 & 0.01 & -1.47 \\ 
  Prior Entry & Entered U.S. once before on a tourist visa & 0.54 & 0.01 & 4.37 \\ 
  Prior Entry & Has visited the U.S. many times before on tourist visas & 0.54 & 0.01 & 4.50 \\ 
  Prior Entry & Spent six months with family members in the U.S & 0.56 & 0.01 & 6.24 \\ 
  Prior Entry & Entered the U.S. once before without legal authorization & 0.37 & 0.01 & -13.96 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}
